\chapter*{Acknowledgments}

\addcontentsline{toc}{chapter}{Acknowledgments}

Throughout this work many people have contributed in some extent to successfully conclude the discussions. This project has been possible thanks to the expertise of Dr. Lucas Sommer, Dr. Tobias Chemnitz at FRM II and Prof. Dr. Peter Müller-Buschbaum. I would like to thank Dr. Lucas Sommer for the extensive discussions on the neutron dosimetry simulations and Dr. Tobias Chemnitz for the continuous supervision of the results of this work.

The multiple simulations have been performed using the Monte Carlo N-Particle code, which has been developed, maintained and delivered by Los Alamos National Laboratory. MCNP models of the radiation source used at MEDAPP were provided by Dr. rer. nat. Harald Breitkrutz, which completed the simulation of the MEDAPP facilities. Without the simulation software, this dissertation would have not been possible. Special thanks to the LANL development team for making the software possible.

The multiple simulations have been automated using an automation tool developed in Python in IntelliJ. This application has significantly facilitated the analysis of data returned by MCNP and made a fundamental contribution to this project. Without this application and the processing infrastructure, it would have not been possible to obtain the results presented in this work within the time span required by the Technical University of Munich.

The calibration measurements of the ionization chambers have been performed at Physikalisch-Technische Bundesanstalt in Braunschweig. The measurements were possible thanks to the collaboration of Dr. Ralf Nolte, Dr. Lucas Sommer and Dr. Tobias Chemnitz over the course of a week to accurately install the devices and set-up the radiation source.

Again, I would like to thank Dr. Tobias Chemnitz for giving me the opportunity to participate in this project and Prof. Dr. Peter Müller-Buschbaum for accepting supervising this thesis. 


\cleardoublepage{}
