\chapter*{Own Publications and Ongoing Projects}
\addcontentsline{toc}{chapter}{Publications and further Projects}
\label{chapter:ownContribution}

\paragraph{Paper publications:}

\begin{itemize}
    \item Sommer, L., Kampfer, S., Chemnitz, T., Breitkreutz, H., Combs, S.E., Wilkens, J.J.: Therapeutic Dose Calculation for a Fission Neutron Source using Pencil Beam Kernels. Physics in Medicine and Biology, submitted in August 2022.
    \item Sommer, L., Chemnitz, T., Kampfer, S., Bausenwein, D., Beimler, A., Kellermeier, M., Sch\"utz, R., Wilkens, J.J., Wagner, F.M.: A New Mulit Leaf Collimator for the Fission Neutron Therapy Facility at FRM II. Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment, to be submitted in August/September 2022.
\end{itemize}

\paragraph{Conference contributions:}
\begin{itemize}
    \item Poster presentation at ESTRO: Development and Validation of a 3D Neutron Therapy Planning System for FRM II. (2020)
\item Oral communication at ECMP: Development and Validation of a 3D Neutron Therapy Planning System for FRM II. (2021)
\item Poster presentation at Dreiländertagung der ÖGMP, DGMP und SGSMP: Implementation and Verification of a 3D Neutron Therapy Planning Software for a Fission Neutron Source. (2021)
\end{itemize}

\paragraph{Contributions as co-author:}
\begin{itemize}
    \item Kumar, R., Sommer, L., Losko, A.S.: Gamma In Addition to Neutron Tomography (GIANT) at the NECTAR instrument. To be submitted in August 2022.
\end{itemize}

\newpage

\paragraph{Ongoing projects:}
\begin{itemize}
    \item Bonete-Wiese, D., Sommer, L., Chemnitz, T., R\"ohrmoser, A., Reiter, C. et al.: Spectral characterization of the modified FRM II beamtube SR-10 using Monte Carlo methods. Ongoing since 2020.
    \item Sommer, L., Moffitt, G.B., Chemnitz, T., Combs, S.E., Wilkens, J.J., Stewart, R.D.: Benchmarking of RBE calculations for the FRM II fission neutron source and retrospective evaluation of calculated biological dose distributions. Ongoing since 2020.
    \item Alexander, F., Sommer, L., Schmid, T., Wilkens, J.J. et al.: A comparison between nanodosimetric and mechanistic inspired approaches to biological effectiveness of neutron radiation. Ongoing since 2021.
    \item Sommer, L., D\"usberg, M., Chemnitz, T., Wilkens, J.J. et al.: Calculation of neutron dose deposition using the the RayStation photon beam model. Ongoing since 2022.
    \item Sommer, L, Bennan, A.B.A., Wikens, J.J., Wahl, N. et al.: Efforts to provide a ready-to-use integration of neutron dose calculation engines for FNT and BNCT into the research treatment planning software matRad. Ongoing since 2022.
\end{itemize}