\chapter{Atmospheric Corrosion of Mg}
Magnesium is the material used to build the outer wall of the PTW TM33054 chamber. It is a suitable material to build ionization chambers because it has a low interaction with neutrons. However, magnesium is very prone to corrosion when it comes into contact with other elements present in the atmosphere. Corrosion is a chemical reaction whose products remain on the surface of the metal where it takes place. In the case of the magnesium chambers, the products are deposited over the internal and external side of the magnesium wall. 

The products have an unknown composition, and they might eventually interact with the radiation that reaches the detector. For this reason, this chapter explores the hypothesis that the interaction of corrosion products can affect the dose measurement of the ionization chamber. Furthermore, this chapter presents evidence supporting the presence of corrosion products.

To investigate this hypothesis, a simulation of the chamber is conducted, including different concentrations of corrosion product layers. The goal here is to compare and understand how the corrosion affects the dose deposition in the sensitive region when the MEDAPP source is applied. 

Additional context regarding the corrosion of the PTW TM33054 ionization chamber is provided in the following subsection. The information provided relies in the doctoral work of Martin Jönnson done at the KTH Royal Institute of Technology in Stockholm, Sweden.

\section{Corrosion of Ionization Chambers}
\input{Master Thesis Manuel Galdon/chapters/Atmospheric corrosion/03_Corrosion of Mg}
\section{X-Ray and Neutron Imaging}
\input{Master Thesis Manuel Galdon/chapters/Atmospheric corrosion/03_Imaging of IC}
\section{Simulated Oxidation Layers}
\input{Master Thesis Manuel Galdon/chapters/Atmospheric corrosion/03_Simulated MgO layers}